Rapid, Unsupervised Generation of Novel Percussive Sounds With A Tractable Virtual Synthesizer

### 2020-01-01 NIME_PAPER/paper.tex
Updates from Overleaf

\end{enumerate}
Automatic programming of virtual synthesizers has also been a topic of interest. In early 2000s, Interactive Genetic Algorithms (IGA's) were utilized for the generation of new sounds with various sound-engines \cite{johnson1999exploring,dahlstedt2001creating}. More recent work by Yee-King et al. \cite{yee2018automatic} used LSTM and genetic algorithms to find the exact parameters used to create a group of sounds. The sounds approximated were made by the same virtual synthesizer, not an external source; making the eventual replication certain, even with random search. Feature matching also appears to not be concerned with the envelope of the sounds, but rather the frequency content within arbitrary time windows. Yet another recent, impressive work by Esling et al. used a large dataset of over 10,000 presets for a commercial VST synthesizer to learn a latent parameter space which can be sampled for creation of new audio. As stated before, our work presents a rapid approximation of percussion sounds with no previous knowledge about the sonic capabilities of our virtual synthesizer.
\section{Implementation}
\label{impl}
\subsection{Design}

>>>>

\end{enumerate}
Automatic programming of virtual synthesizers has also been a topic of interest. In early 2000s, Interactive Genetic Algorithms (IGA's) were utilized for the generation of new sounds with various sound-engines \cite{johnson1999exploring,dahlstedt2001creating}. More recent work by Yee-King et al. \cite{yee2018automatic} used LSTM and genetic algorithms to find the exact parameters used to create a group of sounds. The sounds approximated were made by the same virtual synthesizer, not an external source; making the eventual replication certain, even with random search. Feature matching also appears to not be concerned with the envelope of the sounds, but rather the frequency content within arbitrary time windows. Yet another recent, impressive work by Esling et al. used a large dataset of over 10,000 presets for a commercial VST synthesizer to learn a latent parameter space which can be sampled for creation of new audio \cite{esling2019universal}. As stated before, our work presents a rapid approximation of percussion sounds with no previous knowledge about the sonic capabilities of our virtual synthesizer.
\section{Implementation}
\label{impl}
\subsection{Design}
